### 2021-11-06 Final Doc/Chapters/Chapter1.tex
Scrum added to Ch3

\section{Procedures and Methods of Investigation}
\subsection{Research Paradigm and Methodology Used}
The research aspect of this project will be conducted in accordance with the interpretivist paradigm. The main undertaking of this paradigm is to understand the world and its’ various aspects according to the subjective experiences of people (\cite{kivunja2017understanding}). It is due to this reason that this project uses this paradigm as what each student requires to efficiently learn is subjective to each individual. Kivunja and Kuyini  (2017) further mention that the interpretivist paradigm makes use of subjective epistemology which allows the researcher to analyse the data, which in this project is the principles and qualities that allow for a game to be effective in a learning environment, through their individual cognitive processes. 
\\\\
Kivunja and Kuyini (2017) continue to list certain characteristics of research conducted under this paradigm typically possess. These include the understanding that the social world cannot be fully comprehended from one standpoint which is why this project makes use of various other studies in the compilation of the aforementioned principles and qualities. Another is that knowledge and its’ understanding is developed through the findings of the study itself.
\pagebreak
Design science is a methodology composed of using analytical techniques and can be used according to many paradigms to perform research in the information systems field (\cite{vaishnavi2004design}). This means of research centres on the development of artefacts to better understand certain aspects through the creation of new knowledge and that assessment of an artefacts performance (\cite{vaishnavi2004design}). This methodology was chosen as it provides certain outlines that will allow for the development and analyses of the principles and qualities for a game to be used academically through the creation of such artefact incorporation these qualities into its’ design and development. 
\\\\
Design Science also provides a general structure as to how this project will be completed as shown in Figure 3 below taken from Vaishnavi and Kuechler’s (2004) work. This process allows for the development of an artefact alongside the collection of information and knowledge that can be incorporated into the design and development of the artefact as well as the evaluation of the implementation of the qualities onto the artefact.

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{Figures/ds}
\caption{The Design Science Research Process (\cite{vaishnavi2004design})}
\end{figure}

>>>>

\section{Procedures and Methods of Investigation}
\subsection{Research Paradigm and Methodology Used}
The research aspect of this project will be conducted in accordance with the interpretivist paradigm. The main undertaking of this paradigm is to understand the world and its’ various aspects according to the subjective experiences of people (\cite{kivunja2017understanding}). It is due to this reason that this project uses this paradigm as what each student requires to efficiently learn is subjective to each individual. Kivunja and Kuyini  (2017) further mention that the interpretivist paradigm makes use of subjective epistemology which allows the researcher to analyse the data, which in this project is the principles and qualities that allow for a game to be effective in a learning environment, through their individual cognitive processes. 
\\\\
Kivunja and Kuyini (2017) continue to list certain characteristics of research conducted under this paradigm typically possess. These include the understanding that the social world cannot be fully comprehended from one standpoint which is why this project makes use of various other studies in the compilation of the aforementioned principles and qualities. Another is that knowledge and its’ understanding is developed through the findings of the study itself.
\pagebreak
Design science is a methodology composed of using analytical techniques and can be used according to many paradigms to perform research in the information systems field (\cite{vaishnavi2004design}). This means of research centres on the development of artefacts to better understand certain aspects through the creation of new knowledge and that assessment of an artefacts performance (\cite{vaishnavi2004design}). This methodology was chosen as it provides certain outlines that will allow for the development and analyses of the principles and qualities for a game to be used academically through the creation of such artefact incorporation these qualities into its’ design and development. 
\\\\
Design Science also provides a general structure as to how this project will be completed as shown in Figure \ref{des} below taken from Vaishnavi and Kuechler’s (2004) work. This process allows for the development of an artefact alongside the collection of information and knowledge that can be incorporated into the design and development of the artefact as well as the evaluation of the implementation of the qualities onto the artefact.

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{Figures/ds}
\caption{The Design Science Research Process (\cite{vaishnavi2004design})}
\label{des}
\end{figure}

### 2021-11-06 Final Doc/Chapters/Chapter3.tex
Added Figures to Ch3
Scrum added to Ch3

\section{Artefact Life Cycle Followed and its Different Phases}
% Briefly provide general background on the life cycle that was followed and why it is appropriate to this artefact.

@@

@@

>>>>

\section{Development Methodologies Followed and the Phases}
% Briefly provide general background on the life cycle that was followed and why it is appropriate to this artefact.
\subsection{Artefact}
The development of the artefact, that being the computer game, made use of an Agile approach to its' development. Specifically, the Scrum methodology was used as it allows for incremental and iterative development and testing of the artefact throughout the development life cycle.
\\\\
The Scrum methodology is based on the values and principles set out by the inception of Agile Methodologies in addition to having a foundation of five new values - those being commitment, focus, openness, respect and courage \citep{scrumhermes}. The Scum methodology is intended to be used in a team to facilitate development of a system while also assigning certain roles to the members of a team \citep{scrumhermes}. These roles are:
\begin{itemize}
\begin{multicols}{3}
\item Scrum Master
\item Product Owner
\item Team
\end{multicols}
\end{itemize}
\noindent In the context of this project, the Scum Master role was left unfilled by an individual as
each group member was responsible for the planning and facilitation as a whole and, as such, technically each member acted as a Scrum Master. The Product owner role was held by our supervisor, Prof. Günther Drevin, as they were the one the artefact was being developed for as well as demonstrated to throughout the life cycle. The Team role was filled by the members of the group as previously mentioned.
\\\\
The Scrum methodology makes use of so-called Sprints in the development process with each Sprint being comprised of multiple tasks to be completed. Each Sprint is also comprised of five main activities, those being:
\begin{enumerate}
\begin{multicols}{2}
\item Sprint Planning 1
\item Sprint Planning 2
\item Sprint
\columnbreak
\raggedcolumns
\item Review
\item Retrospective
\end{multicols}
\end{enumerate}

\noindent The development of this project, due to the smaller size of the group, only made use of one initial planning phase for each Sprint and the Review and Retrospective activities were consolidated into discussing what had been done at each Sprint and what should be moved forward to the next Sprint.

\subsection{Article}
The development of the article followed the interpretivist paradigm and made use of a combination of Design Science and the Scrum Agile Methodology throughout the development life cycle. The Scrum Methodology was discussed above and as such only the design science and interpretivist paradigm will be discussed here. 
\\\\

@@

\subsection{Sprint 1: Know the Basics}

\begin{figure}[H]
\centering
\includegraphics[scale=0.33]{Figures/level.png}
\caption{Individual First Level}
\end{figure}

\subsection{Sprint 2: Initial Development}

\begin{figure}[H]
\centering
\includegraphics[scale=0.8]{Figures/floor.png}
\caption{Floor Detection Visualisation (Own Creation)}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale=0.33]{Figures/testold.png}
\caption{Test Scene for Initial Player Movement}
\end{figure}

\subsection{Sprint 3: Full Scale Development}

\begin{figure}[H]
\centering
\includegraphics[scale=0.33]{Figures/portalconcept.png}
\caption{Original Portal Concept}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finporta.png}
  \caption{Main Portal Asset}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finportb.png}
  \caption{Tutorial Specific Re-colouration}
\end{subfigure}
\caption{Finalised Portal Assest}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.45]{Figures/pause.png}
\caption{Pause Menu}
\end{figure}

\subsection{Sprint 4: Build and Publish}

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{Figures/thumb.png}
\caption{The Icon Used for Publication}
\end{figure}

\section{Description of the Development of the Article}
%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.

\subsection{Sprint 1: Research Proposal}

\subsection{Sprint 2: Project Planning}

\subsection{Sprint 3: Sampling and Literature Collection}

\subsection{Sprint 4: Write Article}

\subsection{Sprint 5: Finalise Article}
